---
title: "warmup03-Daniel-delCarpio"
author: "Daniel del Carpio"
date: "February 14, 2019"
output: html_document
---


##1)

```{r}

url <- "https://raw.githubusercontent.com/ucb-stat133/stat133-hws/master/data/nba2018-players.csv"

data_types <- c("character","factor","factor","integer","integer","integer","integer","character","double","integer","integer","integer","integer","integer")

nba <- read.csv(url,sep=",",colClasses = data_types)

str(nba,vec.len = 1)

nba2 <- read.table(url,sep=",",header=TRUE,colClasses = data_types)

str(nba2,vec.len = 1)


print(identical(nba,nba2))

```

##2)

A. The column names disspear turn into V1, V2, V3...

B. They all turn into factors.

C. In read.table header is default set to FALSE, so it does not read correctly, so we have to manually change the header to TRUE.

D. The dataframe without the column classes is about 10000 bytes smaller than the one with the column classes.

E. Turns the dataframe nba into a matrix. The function turns factors to numbers by using their internal codes. 


##3)
```{r}

summary(nba$salary)


hist(nba$salary)

nba$salary2 <- nba$salary / 1000000

hist(nba$salary2)

nba$salary2 <- log(nba$salary2)

hist(nba$salary2)

#Log Transformation does make it a little more symmetrical. The rest of the dsitrubtion is cut off since we are looking closer at most of the bigger values and cutting out the (relatively) very small ones.


low <- nba[nba$salary2 < -3,]
nrow(low)

#There is 8 nba players that have below -3 salary.

low[,c(1,5,4,2,3)]

nba <- nba[-nba$salary2 < -3,]
#nba

dim(nba)


```
##4)

```{r}

summary(nba$points)

hist(nba$points)
```

While points does have a skew to the right, it is not as big as the skew on the salary distribution.

```{r}


nba$points[nba$points==0] <- 0.1

nba$points <- log(nba$points)

hist(nba$points)

#Most of the points are in the 6.5-8 catergories, while very little in the 5.0-5.5 range

```
##5)

```{r}

boxplot(salary2 ~ age, data = nba, xlab='Age',ylab='Salary (in millions)')

#When we look at the boxplots by age, the young age groups like 23-24 are among the lowest salaries, while the 27-30 age gets the median salary, past that age the salries go down, with some outliers (big stars like Lebron/KD)

boxplot(points ~ age, data = nba, xlab='Age',ylab='points')

#Points seems to be about the same with some dips, but once a player reaches 32 they start to slump down and do not come back up. 

age2 <- nba$age
age2[age2 < 19] <- 20

age2 <- cut(age2, breaks=c(20,25,30,max(age2)),labels=c("20-24","25-29","30+"))
summary(age2)

```

##6)
```{r}
palette1<- c("#D4D62A","#4F9D66","#957AB")


#levels(age2$colors)<- palette1

#age2$colors

#age_colors

#plot(salary ~ points, data = nba, log = 'xy',main="", xlab = "Points (log scale)", ylab = "Salary (log$)",col = age_colors, pch = 19, cex = 0.6)

#legend("bottomright", fill = palette1, legend - levels(age2),title = "Age Groups", cex = 0.8)


```

##7)
```{r}

boxplot(salary2 ~ position, data = nba, xlab='Position',ylab='Salary (in millions)')

boxplot(points ~ position, data = nba, xlab='Position',ylab='Points')


#palette2 <- c("#66c2a5","#fcd8d62","8da0cb","e78ac3","a6d854")



```
